Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-10 ms.tex
conclusion section mostly in place

\subsection{Towards a Replacement for SFD}
\label{sec:replace}
%  ---> CIBA
%   ---> do i want a figure illustrating the CIBA problem at high latitude ?
%  ---> zodi
%  ---> more testing needed, in any event, to prove Planck based reddening
%       estimates outperform SFD

@@

@@

>>>>

\subsection{Towards a Replacement for SFD}
\label{sec:replace}
Because of the broad frequency coverage and high angular resolution afforded
by the \PLANCK~HFI full-sky maps, we initially speculated that a \PLANCK~based 
extinction map might easily outperform SFD, the current industry standard data 
product. However, at this point in time, we do not yet recommend that the 
results presented in this work be considered a replacement for SFD in terms of 
optical extinction/reddening estimates.

% CIBA
The CIBA remains a major imperfection that still requires further 
investigation. The CIB anisotropies are very evident in low-dust regions of our
maps of optical depth and predicted dust emission. As described in 
$\S$\ref{sec:mcmc}, we have propagated the CIBA RMS amplitudes and 
inter-frequency covariances into our uncertainty estimates through the 
likelihood function in our MCMC procedure. However, this treatment falls far 
short of actually removing the spatial imprint of the CIBA on our optical depth
and temperature maps. The CIB anisotropies are more prominent in our optical 
depth map relative to that of SFD because of the lower-frequency \PLANCK~maps 
we rely upon to achieve a high-resolution temperature correction.

Imperfect zodi corrections represent a second major limitation of our results.
The prominence of the ecliptic plane in our 
full-sky temperature map of Figure \ref{fig:results} suggests that zodiacal
light subtractions performed on the input maps are not ideal. Our comparisons 
of the maps used in this study against HI emission bear out this notion, and 
show that the imperfect zodi corrections are not limited to \verb|i100| (the
highest frequency for which the zodi should be most problematic), but in fact
are noticeable in all of the HFI ZodiCorrected maps as well. We deemed it 
infeasible to reconsider all of the \PLANCK~zodi corrections in addition to the
3000 GHz zodi correction as a part of this study. Perhaps the forthcoming 
\PLANCK~data release, including data from additional orbits, will effectively 
eliminate any residual zodi problems in the \PLANCK~bands. Under these 
circumstances it might then be worthwhile to consider revising the DIRBE 
100$\mu$m zodi correction provided by SFD.

Irrespective of the notable imperfections in our results, more detailed
comparisons between our reddening estimates here and those of SFD are required 
to determine/quantify which map is superior in particular applications. One 
definitive improvement of our reddening estimates relative to those of SFD is 
our ability to quote reddening uncertainties, which results from the 
probabilistic framework of $\S$\ref{sec:mcmc}. The extinction estimates 
from this work can also be employed as an alternative to those of SFD, to gauge
the impact of dust map choice in a specific application.

% perhaps zodi will just magically be fixed in the forthcoming Planck dta
% release

%   ---> do i want a figure illustrating the CIBA problem at high latitude ?
%  ---> zodi
%  ---> more testing needed, in any event, to prove Planck based reddening
%       estimates outperform SFD

@@

% and should also say that it's worth looking up extinction values here
% to gauge whether results are dependent on choice of dust map

@@

% mention here the idea of getting even higher resolution by folding
% in WISE ?
